### 2015-05-20 doc/notebook/2015-02-26_Bacterial_data_acquisition.Rmd
Finalize through generating final metadata file

```{r get_data, engine="bash"}
wget http://www.arb-silva.de/fileadmin/silva_databases/release_119/ARB_files/SSURef_119_SILVA_14_07_14_opt.arb.tgz
wget http://www.arb-silva.de/fileadmin/silva_databases/release_119/ARB_files/SSURef_119_SILVA_14_07_14_opt.arb.tgz.md5
tar xvzf SSURef_119_SILVA_14_07_14_opt.arb.tgz
```

@@

* Return to Search and Query window
* Change search field to "ARB_color", enter "1", and click the equal sign to be not-equal
* Change the second search field to "tax_rdp" and set it to "*Bacteria*"
* Change the third search field to "tax_rdp" and set it to "*Chloroplast*"
* Set the two Query operators to "and" and hit "Search"
* Hit Mark Listed Unmark Rest (N=1,301,541)
* Click "Write to Fields of Listed", select the "remark" field, and enter "good bacteria"
* Click "Write"
* In main ARB window go File->Export->Export to external format
* Select Compress -> "Vertical Gaps" and fasta_mothur.eft as the format
* Rename `noname.fasta` to `bacteria.fasta`

Now we need the taxonomy information.
* Go Tree -> NDS
* Click "name", "acc", "tax_rdp". The "tax_rdp" field should have 250 characters
* Unclick everything else
* Click "Close"
* Go File->Export->Export fields
* Set the file name to "bacteria.taxonomy" and Column output to "TAB separated"
* Click "SAVE"

@@

```{r get_rdp_names, engine="bash"}
rm -rf RDPClassifier_16S_trainsetNo10_rawtrainingdata* Trainset9_032012.pds.zip

wget -N http://sourceforge.net/projects/rdp-classifier/files/RDP_Classifier_TrainingData/RDPClassifier_16S_trainsetNo10_rawtrainingdata.zip
unzip -o RDPClassifier_16S_trainsetNo10_rawtrainingdata.zip
mv RDPClassifier_16S_trainsetNo10_rawtrainingdata/trainset10_db_taxid.txt ./
rm -rf RDPClassifier_16S_trainsetNo10_rawtrainingdata*
```

@@

```{r format_taxonomy}
tax_data <- read.table(file="bacteria.taxonomy.nds", sep="\t")

@@

#now we need to pull out the taxon names for the sub taxa levels
levels <- read.table(file="trainset10_db_taxid.txt", sep="*", stringsAsFactors=F)
subs <- levels[grep("sub", levels$V5),] #get the sub taxa names
sub.names <- subs$V2

@@

write.table(cbind(seq_names, no.subs.str), "bacteria.tax", row.names=F,
                                                col.names=F, quote=F, sep="\t")
```

@@

```{r get_summary, engine="bash", results="hide", echo=TRUE}
mothur "#summary.seqs(fasta=bacteria.fasta, processors=12)"
```

@@

```{r screen_data, engine="bash"}
mothur "#set.current(processors=8);
        set.dir(input=data/raw, output=data/mothur)
        screen.seqs(fasta=bacteria.fasta, taxonomy=bacteria.tax, start=2000, end=13000, maxambig=2, minlength=1200);"
```

@@

```{r single_cell, engine="bash"}
mothur "#align.seqs(fasta=single_cell.bacteria.fasta, reference=bacteria.good.fasta);
        screen.seqs(fasta=current, start=2000, end=13000, maxambig=2, minlength=1200);
        classify.seqs(fasta=current, reference=trainset10_082014.pds.fasta, taxonomy=trainset10_082014.pds.tax, cutoff=80, processors=8)"
```

@@

```{r pool_data, engine="bash"}
cat bacteria.good.fasta single_cell.bacteria.good.align > all_bacteria.align
cat bacteria.good.tax single_cell.bacteria.good.pds.wang.taxonomy > all_bacteria.taxonomy

mothur "#filter.seqs(fasta=all_bacteria.align, vertical=T, trump=.);
        unique.seqs();
        pre.cluster(fasta=current, name=current, diffs=10);"

#need to make the taxonomy file match the fasta and names files...
cut -f 1 all_bacteria.filter.unique.precluster.names > precluster.accnos
mothur "#get.seqs(taxonomy=all_bacteria.taxonomy, accnos=precluster.accnos)"
```

@@

```{r cluster_data, engine="bash"}
mothur "#cluster.split(fasta=all_bacteria.filter.unique.precluster.fasta, name=all_bacteria.filter.unique.precluster.names, taxonomy=all_bacteria.pick.taxonomy, taxlevel=2, classic=T, processors=8)"
```

@@

We'd like to use some metadata from the database to characterize the changes in
the representation of sequences over time, by environment, methods, etc. The
fields housed within SILVA are available at their [website](http://www.arb-silva.de/fileadmin/arb_web_db/release_115/Fields_description/SILVA_description_of_fields_16_06_2013.htm)
and there is an [FAQ](http://www.arb-silva.de/documentation/faqs/) on their site
as well. There were a number of fields that I didn't think were relevant and
instead focused on 30 fields that I thought could help the cause. I marked these
fields in the NDS feature and extracted them to `metadata.nds`. We need to
tweak this file slightly in R to get it into a format that we can use.

@@

metadata <- read.table(file="data/raw/metadata.nds", sep="\t", stringsAsFactors=FALSE,
                            col.names=metadata_fields, fill=TRUE, na.strings="",
                            quote="")
rownames(metadata) <- paste(metadata$name, metadata$acc, sep=".")
metadata <- metadata[,-c(1,2)]
```

@@

```{r}
bad_accnos_data <- read.table(file="data/mothur/bacteria.bad.accnos", col.names=c("name.accnos", "reason"))
bad_accnos <- bad_accnos_data$name.accnos
metadata_good <- metadata[-c(bad_accnos),]
write.table(metadata_good, file="data/mothur/all_bacteria.good.metadata", quote=F, sep="\t")
```

@@

spread_sheet <- read.xlsx("data/raw/BacterialSSUMetadata.xlsx", sheet=1, startRow=1, colNames=TRUE)
bad_accnos_data <- read.table(file="data/mothur/single_cell.bacteria.bad.accnos", col.names=c("name.accnos", "reason"))
bad_accnos <- bad_accnos_data$name.accnos
spread_sheet_good <- spread_sheet[-c(bad_accnos),]

write.table(spread_sheet_good, file="data/mothur/all_bacteria.good.metadata", quote=F, sep="\t", col.names=F, append=T)
```

>>>>

```{r get_data, engine="bash"}
wget http://www.arb-silva.de/fileadmin/silva_databases/release_119/ARB_files/SSURef_119_SILVA_14_07_14_opt.arb.tgz
wget http://www.arb-silva.de/fileadmin/silva_databases/release_119/ARB_files/SSURef_119_SILVA_14_07_14_opt.arb.tgz.md5
tar xvzf SSURef_119_SILVA_14_07_14_opt.arb.tgz
mv SSURef_119_SILVA_14_07_14_opt.arb SSURef_119_SILVA_14_07_14_opt.arb.tgz.md5 data/references
rm SSURef_119_SILVA_14_07_14_opt.arb.tgz
```

@@

* Return to Search and Query window
* Change search field to "ARB_color", enter "1", and click the equal sign to be not-equal
* Change the second search field to "tax_rdp" and set it to "*Bacteria*"
* Change the third search field to "tax_rdp" and set it to "*Chloroplast*"
* Set the two Query operators to "and" and hit "Search"
* Hit Mark Listed Unmark Rest (N=1,301,541)
* Click "Write to Fields of Listed", select the "remark" field, and enter "good bacteria"
* Click "Write"
* In main ARB window go File->Export->Export to external format
* Select Compress -> "Vertical Gaps" and fasta_mothur.eft as the format
* Rename `noname.fasta` to `data/mothur/bacteria.fasta`

Now we need the taxonomy information.
* Go Tree -> NDS
* Click "name", "acc", "tax_rdp". The "tax_rdp" field should have 250 characters
* Unclick everything else
* Click "Close"
* Go File->Export->Export fields
* Set the file name to "data/mothur/bacteria.taxonomy" and Column output to "TAB separated"
* Click "SAVE"

@@

```{r get_rdp_names, engine="bash"}
wget -N http://sourceforge.net/projects/rdp-classifier/files/RDP_Classifier_TrainingData/RDPClassifier_16S_trainsetNo10_rawtrainingdata.zip
unzip -o RDPClassifier_16S_trainsetNo10_rawtrainingdata.zip
mv RDPClassifier_16S_trainsetNo10_rawtrainingdata/* data/references/
rm -rf RDPClassifier_16S_trainsetNo10_rawtrainingdata*
```

@@

```{r format_taxonomy}
tax_data <- read.table(file="data/mothur/bacteria.taxonomy.nds", sep="\t")

@@

#now we need to pull out the taxon names for the sub taxa levels
levels <- read.table(file="data/references/trainset10_db_taxid.txt", sep="*", stringsAsFactors=F)
subs <- levels[grep("sub", levels$V5),] #get the sub taxa names
sub.names <- subs$V2

@@

write.table(cbind(seq_names, no.subs.str), "data/mothur/bacteria.tax", row.names=F,
                                                col.names=F, quote=F, sep="\t")
```

@@

```{r get_summary, engine="bash", results="hide", echo=TRUE}
mothur "#summary.seqs(fasta=data/mothur/bacteria.fasta, processors=12, outputdir=data/mothur/)"
```

@@

```{r screen_data, engine="bash"}
mothur "#screen.seqs(fasta=data/mothur/bacteria.fasta, taxonomy=data/mothur/bacteria.tax, start=2000, end=13000, maxambig=2, minlength=1200, outputdir=data/mothur/, processors=8);"
```

@@

```{r single_cell, engine="bash"}
wget -N -P data/references/ http://www.mothur.org/w/images/2/24/Trainset10_082014.pds.tgz
tar xvzf data/references/Trainset10_082014.pds.tgz -C data/references/
mv data/references/trainset10_082014.pds/trainset10_082014.* data/references/
rm -rf data/references/trainset10_082014.pds

mothur "#set.dir(output=data/mothur);
        align.seqs(fasta=data/raw/single_cell.bacteria.fasta, reference=data/mothur/bacteria.good.fasta);
        set.dir(input=data/mothur);
        screen.seqs(fasta=current, start=2000, end=13000, maxambig=2, minlength=1200);
        classify.seqs(fasta=current, reference=data/references/trainset10_082014.pds.fasta, taxonomy=data/references/trainset10_082014.pds.tax, cutoff=80, processors=1)"
```

@@

```{r pool_data, engine="bash"}
cat data/mothur/bacteria.good.fasta data/mothur/single_cell.bacteria.good.align > data/mothur/all_bacteria.align
cat data/mothur/bacteria.good.tax data/mothur/single_cell.bacteria.good.pds.wang.taxonomy > data/mothur/all_bacteria.taxonomy

mothur "#set.dir(input=data/mothur, output=data/mothur);
        filter.seqs(fasta=all_bacteria.align, vertical=T, trump=., processors=8);
        unique.seqs();
        pre.cluster(fasta=current, name=current, diffs=10);"

#need to make the taxonomy file match the fasta and names files...
cut -f 1 all_bacteria.filter.unique.precluster.names > precluster.accnos
mothur "#set.dir(input=data/mothur, output=data/mothur);
        get.seqs(taxonomy=all_bacteria.taxonomy, accnos=precluster.accnos)"
```

@@

```{r cluster_data, engine="bash"}
mothur "#set.dir(input=data/mothur, output=data/mothur, seed=1);
        cluster.split(fasta=all_bacteria.filter.unique.precluster.fasta, name=all_bacteria.filter.unique.precluster.names, taxonomy=all_bacteria.pick.taxonomy, taxlevel=2, classic=T, processors=8)"
```

@@

We'd like to use some metadata from the database to characterize the changes in
the representation of sequences over time, by environment, methods, etc. The
fields housed within SILVA are available at their [website](http://www.arb-silva.de/fileadmin/arb_web_db/release_115/Fields_description/SILVA_description_of_fields_16_06_2013.htm)
and there is an [FAQ](http://www.arb-silva.de/documentation/faqs/) on their site
as well. There were a number of fields that I didn't think were relevant and
instead focused on 30 fields that I thought could help the cause. I marked these
fields in the NDS feature and extracted them to
`data/mothur/bacteria.metadata.nds`. We need to tweak this file slightly in R to
get it into a format that we can use.

@@

metadata <- read.table(file="data/mothur/bacteria.metadata.nds", sep="\t", stringsAsFactors=FALSE,
                        col.names=metadata_fields, fill=TRUE, na.strings="",
                        quote="")
rownames(metadata) <- paste(metadata$acc, metadata$name, sep=".")
metadata <- metadata[,-c(1,2)]
```

@@

bad_accnos_data <- read.table(file="data/mothur/bacteria.bad.accnos",
                    col.names=c("name.accnos", "reason"), stringsAsFactors=F)
bad_accnos <- bad_accnos_data$name.accnos
metadata_good <- metadata[-which(rownames(metadata) %in% bad_accnos),]

categories_sheet <- read.xlsx("data/raw/FinalCategories.xlsx", sheet=1, startRow=1, colNames=TRUE)
categories <- categories_sheet[,1]
names(categories) <- categories_sheet[,2]

categories_sheet_missing <- read.xlsx("data/raw/ExtraCategoriesBacteria.xlsx", sheet=1, startRow=1, colNames=FALSE)
categories_missing <- categories_sheet_missing[,"X1"]
names(categories_missing) <- categories_sheet_missing[,"X2"]

categories <- c(categories, categories_missing)

metadata_good$category <- toupper(categories[metadata_good$isolation_source])

extra <- table(metadata_good$isolation_source[is.na(metadata_good$category)])

if(length(extra) == 0){
    write.table(extra, file="missing.txt", row.names=F, col.names=F, sep="\t")
}

write.table(metadata_good, file="data/mothur/bacteria.good.metadata", quote=F, sep="\t")
```

@@

```{r}
spread_sheet <- read.xlsx("data/raw/FormattedBacterialMetadata.xlsx", sheet=1, startRow=1, colNames=TRUE)
rownames(spread_sheet) <- spread_sheet$name
spread_sheet <- spread_sheet[,-c(1,2)]

#need actual category from LSU group
spread_sheet$category <- NA

metadata_genome_id <- gsub(".* (P?SCGC \\S*)", "\\1", spread_sheet$full_name)
metadata_genome_id["SCGC AAA003-L8"] <- "SCGC AAA003-L08"

#need to fix mapping between genome and gene sequences
fasta <- scan("data/mothur/single_cell.bacteria.fasta", what="", quiet=TRUE, sep="\n")
headers <- fasta[grepl(">", fasta)]
seq_numbers <- gsub(">(\\d*) .*", "\\1", headers)
names(seq_numbers) <- gsub(".* (P?SCGC \\S*) .*", "\\1", headers)

#recreate a metadata table using sequence names and spread_sheet
full_spread_sheet <- spread_sheet[names(seq_numbers) %in% metadata_genome_id,]
rownames(full_spread_sheet) <- seq_numbers

#these sequences are missing from metadata file
#metadata_genome_id[! metadata_genome_id %in% names(seq_numbers)]
#probably not a horrible thing since not all genomes could give a 16S rRNA gene
#sequence

bad_accnos_data <- read.table(file="data/mothur/single_cell.bacteria.bad.accnos", col.names=c("name.accnos", "reason"),  stringsAsFactors=FALSE)
bad_accnos <- as.character(bad_accnos_data$name.accnos)

spread_sheet_good <- spread_sheet[-which(rownames(spread_sheet) %in% bad_accnos),]

write.table(spread_sheet_good[,colnames(metadata_good)], file="data/mothur/bacteria.good.metadata", quote=F, sep="\t", col.names=F, append=T)
```

### 2015-05-20 doc/notebook/2015-03-13_Archaeal_data_acquisition.Rmd
Finalize through generating final metadata file

```{r format_taxonomy}
tax_data <- read.table(file="archaea.taxonomy.nds", sep="\t")

@@

write.table(cbind(seq_names, no.subs.str), "archaea.tax", row.names=F,
                                                col.names=F, quote=F, sep="\t")
```

@@

```{r get_summary, engine="bash", results="hide", echo=TRUE}
mothur "#summary.seqs(fasta=archaea.fasta, processors=12)"
```

@@

```{r find_screening_points}
data <- read.table(file="archaea.summary", header=T, row.names=1)
quantile(data$start, probs=seq(0.9,1,0.01))
start <- 2000

@@

```{r screen_data, engine="bash"}
mothur "#set.current(processors=8);
        screen.seqs(fasta=archaea.fasta, taxonomy=archaea.tax, start=2000, end=4058, maxambig=2, maxhomop=8, minlength=900);"
```

@@

```{r single_cell, engine="bash"}
mothur "#align.seqs(fasta=single_cell.archaea.fasta, reference=archaea.good.fasta);
        screen.seqs(fasta=current, start=2000, end=4058, maxambig=2, maxhomop=8, minlength=900);
        classify.seqs(fasta=current, reference=trainset10_082014.pds.fasta, taxonomy=trainset10_082014.pds.tax, cutoff=80, processors=8)"
```

@@

```{r pool_data, engine="bash"}
cat archaea.good.fasta single_cell.archaea.good.align > all_archaea.align
cat archaea.good.tax single_cell.archaea.good.pds.wang.taxonomy > all_archaea.taxonomy

mothur "#filter.seqs(fasta=all_archaea.align, vertical=T, trump=.);
        unique.seqs();
        pre.cluster(fasta=current, name=current, diffs=9);"

#need to make the taxonomy file match the fasta and names files...
cut -f 1 all_archaea.filter.unique.precluster.names > precluster.accnos
mothur "#get.seqs(taxonomy=all_archaea.taxonomy, accnos=precluster.accnos)"
```

@@

```{r cluster_data, engine="bash"}
mothur "#cluster.split(fasta=all_archaea.filter.unique.precluster.fasta, name=all_archaea.filter.unique.precluster.names, taxonomy=all_archaea.pick.taxonomy, taxlevel=2, classic=T, processors=8)"
```

@@

metadata <- read.table(file="archaea_metadata.nds", sep="\t", stringsAsFactors=FALSE,
                            col.names=metadata_fields, fill=TRUE, na.strings="",
                            quote="")
rownames(metadata) <- paste(metadata$name, metadata$acc, sep=".")
metadata <- metadata[,-c(1,2)]
```

@@

```{r}
bad_accnos_data <- read.table(file="archaea.bad.accnos", col.names=c("name.accnos", "reason"))
bad_accnos <- bad_accnos_data$name.accnos
metadata_good <- metadata[-c(bad_accnos),]
write.table(metadata_good, file="all_archaea.good.metadata", quote=F, sep="\t")
```

@@

spread_sheet <- read.xlsx("data/raw/ArchaealSSUMetadata.xlsx", sheet=1, startRow=1, colNames=TRUE)
bad_accnos_data <- read.table(file="data/mothur/single_cell.archaea.bad.accnos", col.names=c("name.accnos", "reason"))
bad_accnos <- bad_accnos_data$name.accnos
spread_sheet_good <- spread_sheet[-c(bad_accnos),]

write.table(spread_sheet_good, file="data/mothur/all_archaea.good.metadata", quote=F, sep="\t", col.names=F, append=T)
```

>>>>

```{r format_taxonomy}
tax_data <- read.table(file="data/mothur/archaea.taxonomy.nds", sep="\t")

@@

write.table(cbind(seq_names, no.subs.str), "data/mothur/archaea.tax", row.names=F,
                                                col.names=F, quote=F, sep="\t")
```

@@

```{r get_summary, engine="bash", results="hide", echo=TRUE}
mothur "#summary.seqs(fasta=data/mothur/archaea.fasta, processors=12)"
```

@@

```{r find_screening_points}
data <- read.table(file="data/mothur/archaea.summary", header=T, row.names=1)
quantile(data$start, probs=seq(0.9,1,0.01))
start <- 2000

@@

```{r screen_data, engine="bash"}
mothur "#set.current(processors=8);
        screen.seqs(fasta=archaea.fasta, taxonomy=archaea.tax, start=2000, end=4058, maxambig=2, maxhomop=8, minlength=900, inputdir=data/mothur/, outputdir=data/mothur/);"
```

@@

```{r single_cell, engine="bash"}
mothur "#set.dir(input=data/mothur, output=data/mothur);
        align.seqs(fasta=single_cell.archaea.fasta, reference=archaea.good.fasta);
        screen.seqs(fasta=current, start=2000, end=4058, maxambig=2, maxhomop=8, minlength=900);
        classify.seqs(fasta=current, reference=data/references/trainset10_082014.pds.fasta, taxonomy=data/references/trainset10_082014.pds.tax, cutoff=80, processors=8)"
```

@@

```{r pool_data, engine="bash"}
cat data/mothur/archaea.good.fasta data/mothur/single_cell.archaea.good.align > data/mothur/all_archaea.align
cat data/mothur/archaea.good.tax data/mothur/single_cell.archaea.good.pds.wang.taxonomy > data/mothur/all_archaea.taxonomy

mothur "#set.dir(input=data/mothur, output=data/mothur);
        filter.seqs(fasta=all_archaea.align, vertical=T, trump=.);
        unique.seqs();
        pre.cluster(fasta=current, name=current, diffs=9);"

#need to make the taxonomy file match the fasta and names files...
cut -f 1 data/mothur/all_archaea.filter.unique.precluster.names > data/mothur/precluster.accnos
mothur "#set.dir(input=data/mothur/, output=data/mothur/);
        get.seqs(taxonomy=all_archaea.taxonomy, accnos=precluster.accnos)"
```

@@

```{r cluster_data, engine="bash"}
mothur "#set.dir(input=data/mothur/, output=data/mothur/);
        cluster.split(fasta=all_archaea.filter.unique.precluster.fasta, name=all_archaea.filter.unique.precluster.names, taxonomy=all_archaea.pick.taxonomy, taxlevel=2, classic=T, processors=8)"
```

@@

metadata <- read.table(file="data/mothur/archaea_metadata.nds", sep="\t",
                        stringsAsFactors=FALSE, col.names=metadata_fields,
                        fill=TRUE, na.strings="", quote="")
rownames(metadata) <- paste(metadata$acc, metadata$name, sep=".")
metadata <- metadata[,-c(1,2)]
```

@@

bad_accnos_data <- read.table(file="data/mothur/archaea.bad.accnos",
                    col.names=c("name.accnos", "reason"), stringsAsFactors=F)
bad_accnos <- bad_accnos_data$name.accnos
metadata_good <- metadata[-which(rownames(metadata) %in% bad_accnos),]

categories_sheet <- read.xlsx("data/raw/FinalCategories.xlsx", sheet=1, startRow=1, colNames=TRUE)
categories <- categories_sheet[,1]
names(categories) <- categories_sheet[,2]

categories_sheet_missing <- read.xlsx("data/raw/ExtraCategoriesArchaea.xlsx", sheet=1, startRow=1, colNames=FALSE)
categories_missing <- categories_sheet_missing[,"X1"]
names(categories_missing) <- categories_sheet_missing[,"X2"]

categories <- c(categories, categories_missing)

metadata_good$category <- toupper(categories[metadata_good$isolation_source])

extra <- table(metadata_good$isolation_source[is.na(metadata_good$category)])

if(length(extra) == 0){
    write.table(extra, file="missing.txt", row.names=F, col.names=F, quote=FALSE,  sep="\t")
}

write.table(metadata_good, file="data/mothur/archaea.good.metadata", quote=F, sep="\t")
```

@@

```{r}
spread_sheet <- read.xlsx("data/raw/FormattedArchaealMetadata.xlsx", sheet=1, startRow=1, colNames=TRUE)
rownames(spread_sheet) <- spread_sheet$name
spread_sheet <- spread_sheet[,-c(1,2)]

#need actual category from LSU group
spread_sheet$category <- NA

metadata_genome_id <- gsub(".* (P?SCGC \\S*).*", "\\1", spread_sheet$full_name)
metadata_genome_id[metadata_genome_id=="SCGC AAA011-J2"] <- "SCGC AAA011-J02"

#need to fix mapping between genome and gene sequences
fasta <- scan("data/mothur/single_cell.archaea.fasta", what="", quiet=TRUE, sep="\n")
headers <- fasta[grepl(">", fasta)]
seq_numbers <- gsub(">(\\d*) .*", "\\1", headers)
parse_header <- gsub(".* (P?SCGC \\S*) .*", "\\1", headers)
parse_header <- gsub(".*SAG-(\\S*) .*", "SCGC \\1", parse_header)

names(seq_numbers) <- parse_header

#recreate a metadata table using sequence names and spread_sheet
full_spread_sheet <- spread_sheet[names(seq_numbers) %in% metadata_genome_id,]
rownames(full_spread_sheet) <- seq_numbers

bad_accnos_data <- read.table(file="data/mothur/single_cell.archaea.bad.accnos", col.names=c("name.accnos", "reason"),  stringsAsFactors=FALSE)
bad_accnos <- as.character(bad_accnos_data$name.accnos)

spread_sheet_good <- spread_sheet[-which(rownames(spread_sheet) %in% bad_accnos),]

write.table(spread_sheet_good[,colnames(metadata_good)], file="data/mothur/archaea.good.metadata", quote=F, sep="\t", col.names=F, append=T)
```
